### 2018-08-10 README.Rmd
code cleanup

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = TRUE,
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  fig.path = "tools/README-"
)
```

@@

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = TRUE,
  cache.path = "tools/README-cache/",
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  fig.path = "man/figures/README-"
)
```

@@

## Individual conditional expectation (ICE) plots

PDPs can be misleading in the presence of substantial interactions [(Goldstein et al., 2015)](https://www.tandfonline.com/doi/full/10.1080/10618600.2014.907095). To overcome this issue Goldstein, Kapelner, Bleich, and Pitkin developed the concept of individual conditional expectation (ICE) plots—available in the [`ICEbox`](https://cran.r-project.org/package=ICEbox) package. ICE plots display the estimated relationship between the response and a predictor of interest for each observation. Consequently, the PDP for a predictor of interest can be obtained by averaging the corresponding ICE curves across all observations. Starting with `pdp` version 0.6.0, ICE and centered ICE (c-ICE) curves can be easily obtained using the `ice` and `center` options; c-ICE plots help visualize heterogeneity in the modeled relationship between observations. Derivative ICE (d-ICE) plots (**coming soon**) help to explore interaction effects.

```{r example-svm-2, fig.width=8, fig.height=4}
# Load required packages
library(ggplot2)  # for additional themes

# ICE and c-ICE curves of diabetes test result on glucose (default logit scale)
ice.glucose <- partial(
  pima.svm, pred.var = "glucose", train = pima, ice = TRUE
)
cice.glucose <- partial(
  pima.svm, pred.var = "glucose", train = pima, ice = TRUE, center = TRUE
)

# Show both plots in one figure
grid.arrange(ncol = 2,
  autoplot(ice.glucose, alpha = 0.1, main = "ICE curves") + theme_light(), 
  autoplot(cice.glucose, alpha = 0.1, main = "c-ICE curves") + theme_light()
)
```

```{r example-rf-3, fig.width=7, fig.height=5}
partial(
  boston.rf, pred.var = "age", ice = TRUE, center = TRUE, plot = TRUE,
  plot.engine = "ggplot2", alpha = 0.1
)
```

## References

Alex Goldstein, Adam Kapelner, Justin Bleich & Emil Pitkin (2014) Peeking Inside the Black Box: Visualizing Statistical Learning With Plots of Individual Conditional Expectation, Journal of Computational and Graphical Statistics, 24:1, 44-65, DOI: 10.1080/10618600.2014.907095
